Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-03-19 docs/supplement.Rnw
fixed all cross-document references

\documentclass[a4paper,hidelinks]{article}
\usepackage{bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,
rotating,caption,subcaption,natbib,appendix,titlesec,multicol,hyperref,verbatim,
bbm,algorithm,algpseudocode,threeparttable,booktabs,mathtools,
dsfont,parskip}

@@

  \section{Introduction}
  This document contains supplementary material to the paper `Adaptive 
  group-regularized logistic elastic net regression'. Section 
  \ref{sec:enetprior} contains extra details on the elastic net prior 
  distribution. Section \ref{sec:objectivefunction} gives the objective 
  function that is maximised in the variational Bayes procedure introduced in
  Section 3 of the Main Document. Section \ref{sec:polyagamma} gives details on
  the P{\'o}lya-Gamma parametrisation introduced in Section 3 of the Main
  Document. The derivations of the variational posterior used in the Main
  Document are shown in Section \ref{sec:variationaldistributions}. Section
  \ref{sec:computationalcomplexity} shows how we may reduce the computational
  complexity of our variational Bayes procedure. Section 
  \ref{sec:expectedloglikelihood} elaborates on the Variational Bayes expected
  joint log likelihood that is maximised to estimate the penalty multipliers as
  explained in Section 3 of the Main Document. The full procedure of the
  proposed method is shown in Section \ref{sec:fullestimationprocedure}. We
  apply our method to a study on microRNAs in colorectal cancer data 
  \cite[]{neerincx_combination_2018} in Section [! section ref here]. Finally, 
  we introduce the ridge and lasso versions of the proposed method in Section
  \ref{sec:evbridgelasso}.

@@

Now we rewrite the calculation of $\c = \begin{bmatrix} c_1 & \cdots & c_n \end{bmatrix} \tr$ as:
\begin{align*}
\c & = \begin{bmatrix} \sqrt{\x_1 \bSigma \x_1 + (\x_1 \tr \bmu)^2} & \cdots & \sqrt{\x_n \bSigma \x_n + (\x_n \tr \bmu)^2} \end{bmatrix} \tr \\
& = \sqrt{\diag \[\X \bSigma \X \tr\] +  \diag \[\X \bmu \bmu \tr \X \tr\]} \\
& = \sqrt{ [(\X \bSigma) \circ \X ] \cdot \ones_{p \times 1} + (\X \bmu) \circ (\X \bmu)}.
\end{align*}
The calculation requires matrix products of complexity $\mathcal{O}(n^2 p)$, Hadamard products of $\mathcal{O}(np)$ and matrix inversions of $\mathcal{O}(n^3)$, such that the total complexity is of $\mathcal{O}(n^2p)$.

@@

\section{Variational Bayes expected joint log likelihood}\label{sec:expectedloglikelihood}
Here, let $\propto$ denote proportionality with respect to $\blambda'$. Then the variational Bayes expected joint log likelihood is derived as follows:
\begin{align*}
\E_{Q} [ \log \L_{\blambda'}(\y, \bomega, \bbeta, \btau) | \blambda'^{(k)} ] &\propto \E_Q [\log \pi_{\blambda'}(\bbeta | \btau) | \blambda'^{(k)}] \propto \sum_{g=1}^G \sum_{j \in \mathcal{G}(g)} \E_Q [\log \pi_{\blambda'}(\beta_j | \tau_j) | \blambda'^{(k)}] \\
& \propto \frac{1}{2} \sum_{g=1}^G \sum_{j \in \mathcal{G}(g)}  \log \lambda'_g - \frac{(1 - \alpha) \lambda}{4} \sum_{g=1}^G \sum_{j \in \mathcal{G}(g)} \lambda'_g \E_Q \( \frac{\tau_j}{\tau_j - 1} \beta_j^2 | \blambda'^{(k)} \) \\ 
& \propto \frac{1}{2} \sum_{g=1}^G |\G(g)|  \log \lambda'_g - \frac{(1 - \alpha) \lambda}{4} \sum_{g=1}^G \lambda'_g d_g^{(k)},
\end{align*}
with the coefficients $d_g^{(k)}$ calculated as:
\begin{align*}
d_g^{(k)} & = \sum_{j \in \mathcal{G}(g)} \E_Q \( \frac{\tau_j}{\tau_j - 1} \beta_j^2 | \blambda'^{(k)} \) \\
& = \sum_{j \in \mathcal{G}(g)} \[1 + \E_{q_{\psi_j}} ( \psi_j^{-1} | \blambda'^{(k)} ) \]  \[ \E_{q_{\beta_j}} ( \beta_j | \blambda'^{(k)} )^2 + \V_{q_{\beta_j}} ( \beta_j | \blambda'^{(k)} ) \] \\
& = \sum_{j \in \mathcal{G}(g)} \[\bSigma^{(k)}_{jj} + (\bmu^{(k)}_j)^2\]\(1 + \alpha \lambda^{1.5} \sqrt{\frac{1 - \alpha}{8 \chi_j^{(k)}}}\).
\end{align*}

\section{Full estimation procedure}\label{sec:fullestimationprocedure}
The expectation and maximisation steps introduced in the Main Document result in a procedure as outlined in Algorithm \ref{alg:summaryalg}:
\begin{algorithm}
	\caption{Group-regularized empirical Bayes elastic net}\label{alg:summaryalg}
	\begin{algorithmic}[h]
		\Require $\X, \y, \G, \alpha, \epsilon_1, \epsilon_2$
		\Ensure $\lambda, \blambda', \bSigma, \bmu$
		\State{Estimate $\lambda$ by cross-validation of the regular elastic net model}
		\While{$|\frac{\blambda'^{(k + 1)} - \blambda'^{(k)}}{\blambda'^{(k)}}| > \epsilon_1$}
		\While{$\underset{ij}{\max} \, |\frac{\bSigma_{ij}^{(k+1)} - \bSigma_{ij}^{(k)}}{\bSigma_{ij}^{(k)}}| > \epsilon_2$ or $\underset{i}{\max} \, |\frac{\bmu_{i}^{(k+1)} - \bmu_{i}^{(k)}}{\bmu_{i}^{(k)}}| > \epsilon_2$}
		\State{Update $\bSigma$, $\bmu$, $c_i$ for $i=1, \dots, n$ and $\chi_j$ for $j=1, \dots, p$ using (3.9) in the Main Document}
		\EndWhile
		\State{Update $\blambda'$ by (3.10) in the Main Document}
		\EndWhile
	\end{algorithmic}
\end{algorithm}

@@

We describe our implementation here for two partitions of the features. To this end, let $(\G_1(1), \dots,\allowbreak \G_1(G_1))$ and $(\G_2(1), \dots, \G_2(G_2))$ denote the two partitions, containing $G_1$ and $G_2$ groups respectively. Furthermore, in the following we assume that the empty sum and empty product evaluate to 0 and 1, respectively. In this two-partition setting we have two penalty multipliers per feature, represented by $\lambda'_{g_1}$ and $\lambda''_{g_2}$, respectively. The generalised frequentist elastic net estimator and corresponding conditional prior are now:
\begin{subequations}\label{eq:multpart}
	\begin{align}
	\hat{\bbeta} &:= \underset{\bbeta}{\argmax} \ell(\y ; \bbeta) -  \frac{\lambda_1}{2} \sum_{g_1=1}^{G_1} \sum_{g_2=1}^{G_2} \sqrt{\lambda'_{g_1} \lambda''_{g_2}} \sum_{\mathclap{\substack{j \in \G_1(g_1) \\ \cap \G_2(g_2)}}} | \beta_j| - \frac{\lambda_2}{2} \sum_{g_1=1}^{G_1} \sum_{g_2=1}^{G_2} \lambda'_{g_1} \lambda''_{g_2} \sum_{\mathclap{\substack{j \in \G_1(g_1) \\ \cap \G_2(g_2)}}} \beta_j^2, \\
	\bbeta | \btau & \sim \prod_{g_1=1}^{G_1} \prod_{g_2=1}^{G_2} \prod_{\substack{j \in \G_1(g_1) \\ \cap \G_2(g_2)}} \mathcal{N} \left(0,\frac{1}{ \lambda'_{g_1} \lambda''_{g_2} \lambda_2} \frac{\tau_j - 1}{\tau_j} \right).
	\end{align}
\end{subequations}
After switching to the parametrisation in \cite{friedman_regularization_2010}, the new penalty multiplier estimates $\blambda'= \begin{bmatrix} \lambda'_1 & \cdots & \lambda'_{G_1} \end{bmatrix} \tr, \blambda''= \begin{bmatrix} \lambda''_1 & \cdots & \lambda''_{G_2} \end{bmatrix} \tr$ are given by:
\begin{subequations}\label{eq:estmultpart}
	\begin{alignat}{2}
	\blambda'^{(k+1)}, \blambda''^{(k+1)} &:= \underset{\blambda', \blambda''}{\argmax} && \Bigg\{ \frac{1}{2} \sum_{g_1=1}^{G_1} |\G_1(g_1)| \log (\lambda'_{g_1}) + \frac{1}{2} \sum_{g_2=1}^{G_2} |\G_2(g_2)| \log (\lambda''_{g_2}) \\ & && - \frac{(1 - \alpha) \lambda}{4} \sum_{g_1=1}^{G_1} \sum_{g_2=1}^{G_2} \lambda'_{g_1} \lambda''_{g_2} d^{(k)}_{g_1 g_2} \Bigg\} \nonumber \\       & \text{subject to } && \prod_{g_1=1}^{G_1} \prod_{g_2=1}^{G_2} (\lambda'_{g_1} \lambda''_{g_2})^{|\G_1(g_1) \cap \G_2(g_2)|} = 1,
	\end{alignat}
\end{subequations}
with the $d_{g_1 g_2}$ terms calculated as $\sum_{\substack{j \in \G_1(g_1) \\ \cap \G_2(g_2)}} \[\bSigma^{(k)}_{jj} + (\bmu^{(k)}_j)^2\]\(1 + \alpha \lambda^{1.5} \sqrt{\frac{1 - \alpha}{8 \chi_j^{(k)}}}\)$. The optimisation in (\ref{eq:estmultpart}) is again a convex problem that is easily solved by some numerical optimisation routine. This method naturally generalises to more than two partitions of the data.

@@

  \section{Simulations}
The quality of feature selection is assessed by Cohen's kappa \cite[]{cohen_coefficient_1960}. This kappa is measures similarity between two sets of categorical values. One set contains the feature selection indicators: $s(j) := \mathbbm{1}\{\hat{\beta}_j \neq 0\}$, while the other set contains the true non-zero feature indicators: $t(j) := \mathbbm{1}\{\beta_j \neq 0\}$. We calculate Cohen's $\kappa$ as:
	\begin{align*}
	\kappa & = \frac{f_o - f_e}{1 - f_e}, \text{ where } f_o = p^{-1}\sum_{j=1}^p \mathbbm{1}\{s(j)=t(j)\} \\ & \text{ and } f_e = p^{-2} \left\{ \(\sum_{j=1}^p s(j)\) \cdot \(\sum_{j=1}^p t(j)\) + \[\sum_{j=1}^p (1 - s(j)) \] \cdot \[\sum_{j=1}^p (1 - t(j)) \]\right\}.
	\end{align*}
	Here, $f_o$ and $f_e$ denote the frequencies of correctly identified and expected correctly identified features, respectively. A positive or negative kappa indicate better and worse feature selection than expected by chance, respectively. In addition, we evaluate estimation accuracy by mean squared error: $\text{MSE} = p^{-1} \sum_{j=1}^p (\beta_j - \hat{\beta}_j)^2$.

@@

  \section{Application to RNAseq in lymph node cancer}
  In addition to the results presented in Section [! section ref here] of the 
  MD, we compared \texttt{gren} to the sparse group lasso (\texttt{SGL}) by 
  \cite{simon_sparse-group_2013} and the group exponential lasso (\texttt{gel}) 
  by \cite{breheny_group_2015}. The original group lasso methods are not 
  designed to deal with overlapping groups, so in addition to using the versions
  that allow for overlapping groups, we 
  cross-tabulated the two co-data partitions to create one paritioning with 25 
  groups for \texttt{cMCP} and \texttt{gel}.
  We use $\alpha \in \{0.05, 0.5, 0.95 \}$ for the
  methods that require this extra tuning parameter. The AUCs and Brier skill 
  scores calculated on the
  validation set are presented in Figures 
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_auc}--
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_briers}
<<lines_rnaseq_lymph_node_metastasis_res1_auc, fig.cap="Estimated AUC for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@

@@

  \section{Application to microRNAs in cervical cancer}
  A deep sequencing analysis on small non-coding ribonucleic acid (microRNAseq) 
  was performed on 24 women with high-grade cervical intraepithelial 
  neoplasia (CIN3) and 32 healthy women for the purpose of finding relevant 
  screening markers for cervical cancer screening. The next generation 
  sequencing analysis resulted in 2,576 transcripts. The data was normalized 
  and pre-processed, rendering 752 transcripts. More details of the
  data sets and the pre-processing steps are found in the supplementary   
  material of \cite{novianti_better_2017}.

@@

\section{Empirical-variational Bayes for the ridge and lasso}\label{sec:evbridgelasso}
\subsection{Ridge regression}
Ridge regression is a special case of the elastic net, that does not include an $L_1$-norm on the parameters. Its estimator is given by:
$$
\hat{\bbeta} := \underset{\bbeta}{\argmax} \ell(\y ; \bbeta) - \frac{\lambda_2}{2} \norm{\bbeta}_2.
$$
The Bayesian version of ridge regression is regression under a Gaussian prior. The generalised version of this prior is:
$$
\bbeta \sim \prod_{g=1}^G \prod_{j \in \G(g)} \N(0,(\lambda_2 \lambda'_g)^{-1}).
$$
Although the posterior is analytically calculated in the linear case, in the logistic case we must approximate it iteratively. The variational distributions in this case are:
\begin{align*}
q^*_{\bbeta} (\bbeta) & \sim \mathcal{N} (\bmu, \bSigma), \\ 
q^*_{\bomega} (\bomega) & \sim \prod_{i=1}^n \mathcal{PG} (m_i, c_i). \\
\end{align*}
The parameters $c_i$ and $\bmu$ remain unchanged compared to the elastic net and are updated, together with $\bSigma$, until convergence:
$$
\bSigma^{t+1} = (\X \tr \bOmega^{(t)} \X + \lambda_2 \bLambda')^{-1}\text{, with } \bOmega^{(t)} = \diag \[ \frac{m_i}{2 c^{(t)}_i} \tanh \( \frac{c^{(t)}_i}{2} \) \].
$$

>>>>

\documentclass[a4paper,hidelinks]{article}
\usepackage{bm,amsmath,amssymb,amsthm,amsfonts,graphics,graphicx,epsfig,
rotating,caption,subcaption,natbib,appendix,titlesec,multicol,verbatim,
bbm,algorithm,algpseudocode,threeparttable,booktabs,mathtools,
dsfont,parskip,xr-hyper,hyperref}
\externaldocument[md-]{manuscript}

@@

  \section{Introduction}\label{sec:introduction}
  This document contains supplementary material to the paper `Adaptive 
  group-regularized logistic elastic net regression'. Section 
  \ref{sec:enetprior} contains extra details on the elastic net prior 
  distribution. Section \ref{sec:objectivefunction} gives the objective 
  function that is maximised in the variational Bayes procedure introduced in
  Section 3 of the Main Document. Section \ref{sec:polyagamma} gives details on
  the P{\'o}lya-Gamma parametrisation introduced in Section 3 of the Main
  Document. The derivations of the variational posterior used in the Main
  Document are shown in Section \ref{sec:variationaldistributions}. Section
  \ref{sec:computationalcomplexity} shows how we may reduce the computational
  complexity of our variational Bayes procedure. Section 
  \ref{sec:expectedloglikelihood} elaborates on the Variational Bayes expected
  joint log likelihood that is maximised to estimate the penalty multipliers as
  explained in Section 3 of the Main Document. The full procedure of the
  proposed method is shown in Section \ref{sec:fullestimationprocedure}. We
  apply our method to a study on microRNAs in colorectal cancer data 
  \cite[]{neerincx_combination_2018} in Section [! section ref here]. Finally, 
  we introduce the ridge and lasso versions of the proposed method in Section
  \ref{sec:evbridgelasso}.

@@

  Now we rewrite the calculation of $\c = \begin{bmatrix} c_1 & \cdots & c_n
  \end{bmatrix} \tr$ as:
  \begin{align*}
    \c & = \begin{bmatrix} \sqrt{\x_1 \bSigma \x_1 + (\x_1 \tr \bmu)^2} & 
    \cdots & \sqrt{\x_n \bSigma \x_n + (\x_n \tr \bmu)^2} \end{bmatrix} \tr \\
    & = \sqrt{\diag \[\X \bSigma \X \tr\] +  
    \diag \[\X \bmu \bmu \tr \X \tr\]} \\
    & = \sqrt{ [(\X \bSigma) \circ \X ] \cdot \ones_{p \times 1} + 
    (\X \bmu) \circ (\X \bmu)}.
  \end{align*}
  The calculation requires matrix products of complexity $\mathcal{O}(n^2 p)$,
  Hadamard products of $\mathcal{O}(np)$ and matrix inversions of $\mathcal{O}
  (n^3)$, such that the total complexity is of $\mathcal{O}(n^2p)$.

@@

  \section{Variational Bayes expected joint log likelihood}
  \label{sec:expectedloglikelihood}
  Here, let $\propto$ denote proportionality with respect to $\blambda'$. Then
  the variational Bayes expected joint log likelihood is derived as follows:
  \begin{align*}
    \E_{Q} [ \log \L_{\blambda'}(\y, \bomega, \bbeta, \btau) | \blambda'^{(k)} ]
    &\propto \E_Q [\log \pi_{\blambda'}(\bbeta | \btau) | \blambda'^{(k)}]
    \propto \sum_{g=1}^G \sum_{j \in \mathcal{G}(g)} \E_Q [\log \pi_{\blambda'}
    (\beta_j | \tau_j) | \blambda'^{(k)}] \\
    & \propto \frac{1}{2} \sum_{g=1}^G \sum_{j \in \mathcal{G}(g)}  
    \log \lambda'_g - \frac{(1 - \alpha) \lambda}{4} \sum_{g=1}^G 
    \sum_{j \in \mathcal{G}(g)} \lambda'_g \E_Q \( \frac{\tau_j}{\tau_j - 1}
    \beta_j^2 | \blambda'^{(k)} \) \\ 
    & \propto \frac{1}{2} \sum_{g=1}^G |\G(g)|  \log \lambda'_g - 
    \frac{(1 - \alpha) \lambda}{4} \sum_{g=1}^G \lambda'_g d_g^{(k)},
  \end{align*}
  with the coefficients $d_g^{(k)}$ calculated as:
  \begin{align*}
    d_g^{(k)} & = \sum_{j \in \mathcal{G}(g)} \E_Q \( \frac{\tau_j}{\tau_j - 1}
    \beta_j^2 | \blambda'^{(k)} \) \\
    & = \sum_{j \in \mathcal{G}(g)} \[1 + \E_{q_{\psi_j}} 
    ( \psi_j^{-1} | \blambda'^{(k)} ) \]  \[ \E_{q_{\beta_j}} 
    ( \beta_j | \blambda'^{(k)} )^2 + \V_{q_{\beta_j}} 
    ( \beta_j | \blambda'^{(k)} ) \] \\
    & = \sum_{j \in \mathcal{G}(g)} \[\bSigma^{(k)}_{jj} + 
    (\bmu^{(k)}_j)^2\]\(1 + \alpha \lambda^{1.5} 
    \sqrt{\frac{1 - \alpha}{8 \chi_j^{(k)}}}\).
  \end{align*}

  \section{Full estimation procedure}\label{sec:fullestimationprocedure}
  The expectation and maximisation steps introduced in the Main Document result
  in a procedure as outlined in Algorithm \ref{alg:summaryalg}:
  \begin{algorithm}
    \caption{Group-regularized empirical Bayes elastic net}
    \label{alg:summaryalg}
	  \begin{algorithmic}[h]
		  \Require $\X, \y, \G, \alpha, \epsilon_1, \epsilon_2$
		  \Ensure $\lambda, \blambda', \bSigma, \bmu$
		  \State{Estimate $\lambda$ by cross-validation of the regular elastic net
		  model}
		  \While{$|\frac{\blambda'^{(k + 1)} - \blambda'^{(k)}}{\blambda'^{(k)}}| >
		  \epsilon_1$}
		  \While{$\underset{ij}{\max} \, |\frac{\bSigma_{ij}^{(k+1)} - 
		  \bSigma_{ij}^{(k)}}{\bSigma_{ij}^{(k)}}| > \epsilon_2$ or 
		  $\underset{i}{\max} \, |\frac{\bmu_{i}^{(k+1)} - 
		  \bmu_{i}^{(k)}}{\bmu_{i}^{(k)}}| > \epsilon_2$}
		  \State{Update $\bSigma$, $\bmu$, $c_i$ for $i=1, \dots, n$ and $\chi_j$ 
		  for $j=1, \dots, p$ using (3.9) in the Main Document}
		  \EndWhile
		  \State{Update $\blambda'$ by (3.10) in the Main Document}
		  \EndWhile
	  \end{algorithmic}
  \end{algorithm}

@@

  We describe our implementation here for two partitions of the features. To
  this end, let $(\G_1(1), \dots,\allowbreak \G_1(G_1))$ and $(\G_2(1), \dots,
  \G_2(G_2))$ denote the two partitions, containing $G_1$ and $G_2$ groups
  respectively. Furthermore, in the following we assume that the empty sum and
  empty product evaluate to 0 and 1, respectively. In this two-partition setting
  we have two penalty multipliers per feature, represented by $\lambda'_{g_1}$
  and $\lambda''_{g_2}$, respectively. The generalised frequentist elastic net
  estimator and corresponding conditional prior are now:
  \begin{subequations}\label{eq:multpart}
	  \begin{align}
	    \hat{\bbeta} &:= \underset{\bbeta}{\argmax} \ell(\y ; \bbeta) -  
	    \frac{\lambda_1}{2} \sum_{g_1=1}^{G_1} \sum_{g_2=1}^{G_2} 
	    \sqrt{\lambda'_{g_1} \lambda''_{g_2}} 
	    \sum_{\mathclap{\substack{j \in \G_1(g_1) \\ \cap \G_2(g_2)}}} | \beta_j|
	    - \frac{\lambda_2}{2} \sum_{g_1=1}^{G_1} \sum_{g_2=1}^{G_2} \lambda'_{g_1}
	    \lambda''_{g_2} \sum_{\mathclap{\substack{j \in \G_1(g_1) \\ 
	    \cap \G_2(g_2)}}} \beta_j^2, \\
	    \bbeta | \btau & \sim \prod_{g_1=1}^{G_1} \prod_{g_2=1}^{G_2} 
	    \prod_{\substack{j \in \G_1(g_1) \\ \cap \G_2(g_2)}} 
	    \mathcal{N} \left(0,\frac{1}{ \lambda'_{g_1} \lambda''_{g_2} \lambda_2}
	    \frac{\tau_j - 1}{\tau_j} \right).
	  \end{align}
  \end{subequations}
  After switching to the parametrisation in \cite{friedman_regularization_2010},
  the new penalty multiplier estimates $\blambda'= \begin{bmatrix} \lambda'_1 &
  \cdots & \lambda'_{G_1} \end{bmatrix} \tr, \blambda''= \begin{bmatrix}
  \lambda''_1 & \cdots & \lambda''_{G_2} \end{bmatrix} \tr$ are given by:
  \begin{subequations}\label{eq:estmultpart}
	  \begin{alignat}{2}
	    \blambda'^{(k+1)}, \blambda''^{(k+1)} &:= \underset{\blambda', \blambda''}
	    {\argmax} && \Bigg\{ \frac{1}{2} \sum_{g_1=1}^{G_1} |\G_1(g_1)| 
	    \log (\lambda'_{g_1}) + \frac{1}{2} \sum_{g_2=1}^{G_2} |\G_2(g_2)| 
	    \log (\lambda''_{g_2}) \\ & && - \frac{(1 - \alpha) \lambda}{4} 
	    \sum_{g_1=1}^{G_1} \sum_{g_2=1}^{G_2} \lambda'_{g_1} \lambda''_{g_2} 
	    d^{(k)}_{g_1 g_2} \Bigg\} \nonumber \\       
	    & \text{subject to } && \prod_{g_1=1}^{G_1} \prod_{g_2=1}^{G_2} 
	    (\lambda'_{g_1} \lambda''_{g_2})^{|\G_1(g_1) \cap \G_2(g_2)|} = 1,
	  \end{alignat}
  \end{subequations}
  with the $d_{g_1 g_2}$ terms calculated as $\sum_{\substack{j \in \G_1(g_1) \\
  \cap \G_2(g_2)}} \[\bSigma^{(k)}_{jj} + (\bmu^{(k)}_j)^2\]\(1 + \alpha
  \lambda^{1.5} \sqrt{\frac{1 - \alpha}{8 \chi_j^{(k)}}}\)$. The optimisation in
  (\ref{eq:estmultpart}) is again a convex problem that is easily solved by some
  numerical optimisation routine. This method naturally generalises to more than
  two partitions of the data.

@@

  \section{Simulations}\label{sec:simulations}
  The quality of feature selection is assessed by Cohen's kappa 
  \cite[]{cohen_coefficient_1960}. This kappa is measures similarity between two
  sets of categorical values. One set contains the feature selection indicators:
  $s(j) := \mathbbm{1}\{\hat{\beta}_j \neq 0\}$, while the other set contains
  the true non-zero feature indicators: $t(j) := \mathbbm{1}\{\beta_j \neq 0\}$.
  We calculate Cohen's $\kappa$ as:
	\begin{align*}
	  \kappa & = \frac{f_o - f_e}{1 - f_e}, \text{ where } f_o = p^{-1}
	  \sum_{j=1}^p \mathbbm{1}\{s(j)=t(j)\} \\ & \text{ and } f_e = p^{-2} 
	  \left\{ \(\sum_{j=1}^p s(j)\) \cdot \(\sum_{j=1}^p t(j)\) + 
	  \[\sum_{j=1}^p (1 - s(j)) \] \cdot \[\sum_{j=1}^p (1 - t(j)) \]\right\}.
	\end{align*}
	Here, $f_o$ and $f_e$ denote the frequencies of correctly identified and
	expected correctly identified features, respectively. A positive or negative
	kappa indicate better and worse feature selection than expected by chance,
	respectively. In addition, we evaluate estimation accuracy by mean squared
	error: $\text{MSE} = p^{-1} \sum_{j=1}^p (\beta_j - \hat{\beta}_j)^2$.

@@

  \section{Application to RNAseq in lymph node cancer}
  \label{sec:lymphnode}
  In addition to the results presented in Section [! section ref here] of the 
  MD, we compared \texttt{gren} to the sparse group lasso (\texttt{SGL}) by 
  \cite{simon_sparse-group_2013} and the group exponential lasso (\texttt{gel}) 
  by \cite{breheny_group_2015}. The original group lasso methods are not 
  designed to deal with overlapping groups, so in addition to using the versions
  that allow for overlapping groups, we 
  cross-tabulated the two co-data partitions to create one paritioning with 25 
  groups for \texttt{cMCP} and \texttt{gel}.
  We use $\alpha \in \{0.05, 0.5, 0.95 \}$ for the
  methods that require this extra tuning parameter. The AUCs and Brier skill 
  scores calculated on the
  validation set are presented in Figures 
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_auc}--
  \ref{fig:lines_rnaseq_lymph_node_metastasis_res1_briers}
<<lines_rnaseq_lymph_node_metastasis_res1_auc, fig.cap="Estimated AUC for the lymph node cancer example.", out.width="100%", fig.asp=1>>=
@

@@

  \section{Application to microRNAs in cervical cancer}\label{sec:cervical}
  A deep sequencing analysis on small non-coding ribonucleic acid (microRNAseq) 
  was performed on 24 women with high-grade cervical intraepithelial 
  neoplasia (CIN3) and 32 healthy women for the purpose of finding relevant 
  screening markers for cervical cancer screening. The next generation 
  sequencing analysis resulted in 2,576 transcripts. The data was normalized 
  and pre-processed, rendering 752 transcripts. More details of the
  data sets and the pre-processing steps are found in the supplementary   
  material of \cite{novianti_better_2017}.

@@

  \section{Empirical-variational Bayes for the ridge and lasso}
  \label{sec:evbridgelasso}
  \subsection{Ridge regression}
  Ridge regression is a special case of the elastic net, that does not include
  an $L_1$-norm on the parameters. Its estimator is given by:
  $$
  \hat{\bbeta} := \underset{\bbeta}{\argmax} \ell(\y ; \bbeta) - 
  \frac{\lambda_2}{2} \norm{\bbeta}_2.
  $$
  The Bayesian version of ridge regression is regression under a Gaussian prior.
  The generalised version of this prior is:
  $$
  \bbeta \sim \prod_{g=1}^G \prod_{j \in \G(g)} 
  \N(0,(\lambda_2 \lambda'_g)^{-1}).
  $$
  Although the posterior is analytically calculated in the linear case, in the
  logistic case we must approximate it iteratively. The variational 
  distributions in this case are:
  \begin{align*}
    q^*_{\bbeta} (\bbeta) & \sim \mathcal{N} (\bmu, \bSigma), \\ 
    q^*_{\bomega} (\bomega) & \sim \prod_{i=1}^n \mathcal{PG} (m_i, c_i). \\
  \end{align*}
  The parameters $c_i$ and $\bmu$ remain unchanged compared to the elastic net
  and are updated, together with $\bSigma$, until convergence:
  $$
  \bSigma^{t+1} = (\X \tr \bOmega^{(t)} \X + \lambda_2 \bLambda')^{-1}
  \text{, with } \bOmega^{(t)} = \diag \[ \frac{m_i}{2 c^{(t)}_i} 
  \tanh \( \frac{c^{(t)}_i}{2} \) \].
  $$
